# Background
Load necessary libraries and source functions.
```{r}
library(tidyverse)
source("../R/moving-average.R")
```

# Data
Load data for the four rivers using read_csv.
```{r}
prm <- read_csv(
  "data/RioMameyesPuenteRoto.csv",
  na = c("", "NA")
)
bq1 <- read_csv(
  "data/QuebradaCuenca1-Bisley.csv",
  na = c("", "NA")
)
bq2 <- read_csv(
  "data/QuebradaCuenca2-Bisley.csv",
  na = c("", "NA")
)
bq3 <- read_csv(
  "data/QuebradaCuenca3-Bisley.csv",
  na = c("", "NA")
)
```

# Methods

Use the moving_average() function to determine the moving average for each ion within each of the four rivers and pivot the data frame to be longer.
```{r}

# keep only the necessary cols
prm <- prm |>
  select(Sample_ID, Sample_Date, K, `NH4-N`, `NO3-N`, Mg, Ca)

bq1_ <- bq1 |>
  select(Sample_ID, Sample_Date, K, `NH4-N`, `NO3-N`, Mg, Ca)

bq2 <- bq2 |>
  select(Sample_ID, Sample_Date, K, `NH4-N`, `NO3-N`, Mg, Ca)

bq3 <- bq3 |>
  select(Sample_ID, Sample_Date, K, `NH4-N`, `NO3-N`, Mg, Ca)


# process the data for the moving averages (9 wk avgs)
prm_moving_avg <- moving_average(prm)
bq1_moving_avg <- moving_average(bq1)
bq2_moving_avg <- moving_average(bq2)
bq3_moving_avg <- moving_average(bq3)

# pivot longer
# pivot longer
prm_longer <- pivot_longer(
  prm_moving_avg,
  cols = k_mgl:ca_mgl,
  names_to = "Ion",
  values_to = "Concentration"
)
bq1_longer <- pivot_longer(
  bq1_moving_avg,
  cols = k_mgl:ca_mgl,
  names_to = "Ion",
  values_to = "Concentration"
)

bq2_longer <- pivot_longer(
  bq2_moving_avg,
  cols = k_mgl:ca_mgl,
  names_to = "Ion",
  values_to = "Concentration"
)

bq3_longer <- pivot_longer(
  bq3_moving_avg,
  cols = k_mgl:ca_mgl,
  names_to = "Ion",
  values_to = "Concentration"
)

# add a descriptive column for stream name before binding
prm_longer <- mutate(prm_longer, Stream = "PRM")
bq1_longer <- mutate(bq1_longer, Stream = "BQ1")
bq2_longer <- mutate(bq2_longer, Stream = "BQ2")
bq3_longer <- mutate(bq3_longer, Stream = "BQ3")


# Join stream data frames
all_streams <- rbind(prm_longer, bq1_longer, bq2_longer, bq3_longer)
```

# Results

To view the updates results, run this ggplot code chunk where we us the longer data frame to view the stream chemistry by the concentration of each ion.
``` {r}
# csv output
write_csv(all_streams, "output/all_streams.csv")

# visualize using ggplot
ggplot(
  all_streams,
  mapping = aes(
    x = window_start,
    y = Concentration,
    linetype = Stream
  )
) +
  geom_line() +
  facet_wrap(
    vars(Ion),
    scales = 'free_y',
    ncol = 1,
    strip.position = "left"
  ) +
  theme_bw() +
  labs(
    x = "Years",
    y = "Concentration",
    title = "Ion Concentrations in Streams"
  ) +
  geom_vline(
    xintercept = ymd("1989-09-08"),
    linetype = "dashed",
    color = "black"
  )
```
 