# Background
Load necessary libraries and source functions.
```{r}
library(tidyverse)
source("../R/moving-average.R")
```

# Data
Load data for the four rivers using read_csv.
```{r}
prm <- read_csv(
  "../data/knb-lter-luq.20.4923064/RioMameyesPuenteRoto.csv",
  na = c("", "NA")
)
bq1 <- read_csv(
  "../data/knb-lter-luq.20.4923064/QuebradaCuenca1-Bisley.csv",
  na = c("", "NA")
)
bq2 <- read_csv(
  "../data/knb-lter-luq.20.4923064/QuebradaCuenca2-Bisley.csv",
  na = c("", "NA")
)
bq3 <- read_csv(
  "../data/knb-lter-luq.20.4923064/QuebradaCuenca3-Bisley.csv",
  na = c("", "NA")
)
```

# Methods

Use the moving_average() function to determine the moving average for each ion within each of the four rivers and pivot the data frame to be longer.
```{r}
# process the data for the moving averages (9 wk avgs)
prm_moving_avg <- moving_average(prm)
glimpse(prm_moving_avg)

# pivot longer
prm_longer <- pivot_longer(
  prm_moving_avg,
  cols = k_mgl:ca_mgl,
  names_to = "Ion",
  values_to = "Concentration"
)
```

# Results

To view the updates results, run this ggplot code chunk where we us the longer data frame to view the stream chemistry by the concentration of each ion.
``` {r}
# visualize using ggplot
ggplot(
  prm_longer,
  mapping = aes(
    x = window_start,
    y = Concentration,
    color = Ion
  )
) +
  geom_line() +
  facet_wrap(~Ion, scales = "free")
```
 